---
title: "Comprehensive example of grading with gradetools"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Comprehensive example of grading with gradetools}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(gradetools)
```

For this vignette we assume that you have already familiarized yourself with the basic functionalities of gradetools (see the vignette "how-to-grade-with-gradetools"). `assist_grading()` and `assist_team_grading()` are essentially wrappers for `assist_advanced_grading()`, so all functionalities available in those functions are also available in this function.


The purpose of this vignette is to provide a different grading scenario which involves:  

  - Project instead of homework or quiz
  - Team grading
  - Assignments on Github
  - Multiple files per submission
  - Pushing issues and feedback to GitHub
  

## Cloning project repos  

This vignette uses two GitHub repositories (repos) from the [gradetools-test-course](https://github.com/gradetools-test-course) Github organization:
 
  - [final-project-team-poisson](https://github.com/gradetools-test-course/final-project-team-poisson) for one team submission.
  - [final-project-team-gamma](https://github.com/gradetools-test-course/final-project-team-gamma) for the second team submission.


## Creating issues and grading assignments  

This vignette assumes knowledge on how to grade with gradetools. We will note an issue on one submission and skip grading the rest of the submissions. 


## Credits

The extended functionalities for assignments managed using GitHub were possible thanks to the functions in the [ghclass](https://rundel.github.io/ghclass/index.html) package.

The final project submissions were made from the [GitHub repository template](https://github.com/mine-cetinkaya-rundel/ds-final-project) accompanying "The 5Ws and 1H of Term Projects in the Introductory Data Science Classroom" by Çetinkaya-Rundel, Dogucu, and Rummerfield (2022).